Glacial flows, simulated faster

### 2023-06-07 talk-iu/slides.tex
I am going with this version

\begin{itemize}
\item direct attack on the NCP-coupled-to-Stokes problem, to get an optimal ($\beta=0$) solver, seems to require a \alert{multilevel} solver for \alert{variational inequalities} (VIs)
\item but in the \alert{non-local residual} case
    \begin{itemize}
    \item[$\circ$] application of the smoother needs to reduce the NCP residual from the surface-motion term $\Phi(s) = - \bu|_s\cdot \bn_s$, where $\bu|_s$ is evaluated from a scalable Stokes solver
    \end{itemize}
\item this seems not to exist, but we are starting to work on it \dots
\end{itemize}
\end{frame}

@@

a multilevel method for box constrained NCPs and VIs
\end{block}

@@

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item results below show FASCD F-cycles give optimal ($\beta=0$) performance for the SIA problem
    \begin{itemize}
    \item[$\circ$] \emph{iterations} counts number of V-cycles after F-cycle ``ramp''
    \item[$\circ$] \emph{time} is for 4 core runs on my laptop
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\hfill \input{fullcycle.tex}
\end{column}
\end{columns}

\bigskip
\begin{center}
\begin{tabular}{c|r|c|r}
\emph{levels} & $N$ & \emph{iterations} & \emph{time} (s) \\ \hline
\input{siaresults.txt} \hspace{-2.2mm}
\end{tabular}
\end{center}
\end{frame}

>>>>

\begin{itemize}
\item direct attack on the NCP-coupled-to-Stokes problem, to get an optimal ($\beta=0$) solver, seems to require a \alert{multilevel} solver for \alert{variational inequalities} (VIs)
\item but in the \alert{non-local residual} case
    \begin{itemize}
    \item[$\circ$] application of the smoother needs to reduce the NCP residual from the surface-motion term $\Phi(s) = - \bu|_s\cdot \bn_s$, where $\bu|_s$ is evaluated from a scalable Stokes solver
    \end{itemize}
\item this seems not to exist, but we are making progress \dots
\end{itemize}
\end{frame}

@@

a multilevel method for box-constrained NCPs and VIs
\end{block}

@@

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item results below show FASCD F-cycles give optimal ($\beta=0$) performance for the SIA NCP problem
    \begin{itemize}
    \item[$\circ$] \emph{iterations} $=$ number of V-cycles after F-cycle ``ramp''
    \item[$\circ$] \emph{time} is for 4-core runs on my laptop
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\hfill \input{fullcycle.tex}
\end{column}
\end{columns}

\bigskip
\begin{center}
\begin{tabular}{c|r|c|r}
\emph{levels} & $m$ & \emph{iterations} & \emph{time} (s) \\ \hline
\input{siaresults.txt} \hspace{-2.2mm}
\end{tabular}
\end{center}
\end{frame}
